prolfqua - A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-06-01 inst/MyArticle/paper.Rmd

 \begin{quote}
``Es ist nicht das Wissen, sondern das Lernen, nicht das Besitzen, sondern das Erwerben, nicht das Dasein, sondern das Hinkommen, was den größten Genuß gewährt.''

Carl Friedrich Gauß
 \end{quote}

>>>>

\begin{quote}
To paraphrase provocatively, `machine learning is statistics minus any checking of models and assumptions'.

-- Brian D. Ripley (about the difference between machine learning and statistics) useR! 2004, Vienna (May 2004).
\end{quote}
